### 2020-12-18 Thesis-Chapter7-PathsForward.tex
Minor editorial improvements

The interests of security, safety, privacy, and trust converge on the issue of encryption and \acl{EA}, creating a
\ac{wicked-prob}. The importance of information security is increasing as more data, business, and infrastructure goes
online. The technical community is struggles with security. Even for the most well-equipped organizations, thwarting the
average attacker is difficult, and the best attacker, impossible. \Ac{cryptography} plays a fundamental role in
security, yet it remains a controversial technology due to its simultaneous role in enabling unprecedented privacy.

@@

Second, \ac{EA} history teaches that the current situation is temporary. This is true of all \acp{wicked-prob}, but
especially for encryption policy due to rapidly evolving technology and a vulnerability arms race between device
manufacturers and lawful hackers. The circumstances are sure to change, and the conclusion that \ac{EA} is unjustified
may change as well.

@@

Further research into \ac{EA} is justified by the additions to the threat model and the instability of present
circumstances. Fortunately, developments in secure hardware mark real progress in the search for acceptably secure
\ac{EA}. Secure hardware technology is not perfect; on its own, it does not resolve the numerous challenges that
full-fledged \ac{EA} proposals must overcome. However, \ac{EA} proposals leveraging secure hardware, such as device
escrow for \acl{DAR}, represent progress. They offer transparency, protection from \ac{masssurv}, and \acl{LE} utility
while remaining somewhat secure.

@@

It is the responsibility of the technical community to accept and address the substantial role technology plays in
current policy issues, such as encryption, automation, and misinformation. Government sometimes suggests that the tech
community simply needs to try harder. Because these are not tame problems, the tech world is absolutely right that
simply trying harder will not work---but that does not mean they cannot deal with them. The tech industry is optimized
to address tame problems, but it must now turn its financial and intellectual capital towards strategies designed for
\acp{wicked-prob}. In order to do so, the tech industry must involve people of diverse backgrounds and values in design
and investment decisions. Designers must consider the ways in which their products could be abused and business models
must be responsive to evolving conditions.

@@

One of the largest non-technical risks of \ac{EA} is its potential abuse by jurisdictions with poor rule of law. This is
the reason transparency is a goal of the threat model. Device key escrow can achieve partial transparency through
physical possession and disassembly requirements. Ideally, usage of \ac{EA} mechanisms would be fully auditable to the
public through inherent technical mechanisms. This could be improved for \acl{DAR} and must be improved for \acl{DIM}.

@@

Fortunately, this research is already happening to some degree, but more is necessary. Some \ac{EA} proposals include
built-in transparency and distributed trust mechanisms \cite{goos_oblivious_1996} \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. Like device key escrow, approaches such as these hold promise, but must be better
understood before they could be implemented. Even while these problems remain unsolved, technologists must provide clear
security advice and speak out against bad policy.

@@

The goal of this thesis is to establish encryption and \ac{EA} as a \ac{wicked-prob}, to analyze the debate, and to
evaluate the security of current \ac{EA} technology. I aim to advance the discussion with a strategy to tackle
\acp{wicked-prob}, additions to the cryptosystem threat model, and detailed analysis of a modern proposal. The strategy
is based on the \acl{OODAloop}. In those terms, this paper serves to \ii{observe} and \ii{orient}. Technologists,
policymakers, and common people must \ii{decide} and \ii{act}. Confronting these issues may be difficult, but the future
of security, safety, and privacy depends on finding an acceptable solution where no perfect solution exists.

>>>>

The interests of security, safety, privacy, and trust converge on the issue of encryption and \acl{EA}, creating a
\ac{wicked-prob}. The importance of information security is increasing as more data, business, and infrastructure goes
online. The technical community struggles with security. Even for the most well-equipped organizations, thwarting the
average attacker is difficult, and the best attacker, impossible. \Ac{cryptography} plays a fundamental role in
security, yet it remains a controversial technology due to its simultaneous role in enabling unprecedented privacy.

@@

Second, \ac{EA} history teaches that the current situation is temporary. This is true of all \acp{wicked-prob}, but
especially for encryption policy due to rapidly evolving technology and a vulnerability arms race between device
manufacturers and lawful hackers. Circumstances are sure to change, and the conclusion that \ac{EA} is unjustified may
change as well.

@@

Further research into \ac{EA} is warranted due to the additions to the threat model and the instability of present
circumstances. Fortunately, developments in secure hardware mark real progress in the search for acceptably secure
\ac{EA}. Secure hardware technology is not perfect; on its own, it does not resolve the numerous challenges that
full-fledged \ac{EA} proposals must overcome. However, \ac{EA} proposals leveraging secure hardware, such as device
escrow for \acl{DAR}, represent progress. They offer transparency, protection from \ac{masssurv}, and \acl{LE} utility
while remaining somewhat secure.

@@

It is the responsibility of the technical community to accept and address the substantial role technology plays in
current policy issues, such as encryption, automation, and misinformation. Government sometimes suggests that the tech
world simply needs to try harder. Because these are not tame problems, the tech world is absolutely right that
simply trying harder will not work---but that does not mean they cannot deal with them. The tech industry is optimized
to address tame problems, but it must now turn its financial and intellectual capital towards strategies designed for
\acp{wicked-prob}. In order to do so, the tech industry must involve people of diverse backgrounds and values in design
and investment decisions. Designers must consider the ways in which their products could be abused, and business models
must be responsive to evolving conditions.

@@

One of the largest non-technical risks of \ac{EA} is its potential abuse by jurisdictions with poor rule of law. This is
the reason transparency is a goal of the threat model. Device key escrow can achieve partial transparency through
physical possession and disassembly requirements. Ideally, usage of \ac{EA} mechanisms would be fully auditable to the
public through inherent technical mechanisms. This can be improved for \acl{DAR} and must be improved for \acl{DIM}.

@@

Fortunately, this research is already happening to some degree, though more is necessary. Some \ac{EA} proposals include
built-in transparency and distributed trust mechanisms \cite{goos_oblivious_1996} \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. Like device key escrow, approaches such as these hold promise, but must be better
understood before they could be implemented. Even while these problems remain unsolved, technologists must provide clear
security advice and speak out against bad policy.

@@

The goal of this thesis is to establish encryption policy as a \ac{wicked-prob}, to analyze the debate, and to evaluate
the security of current \ac{EA} technology. I aim to advance the discussion with a strategy to tackle \acp{wicked-prob},
additions to the cryptosystem threat model, and detailed analysis of a modern proposal. The strategy is based on the
\acl{OODAloop}. In those terms, this paper serves to \ii{observe} and \ii{orient}. Technologists, policymakers, and
common people must \ii{decide} and \ii{act}. Confronting these issues may be difficult, but the future of security,
safety, and privacy depends on finding an acceptable solution where no perfect solution exists.
